\documentclass[10pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}

\usepackage[scale=.9, top=1cm]{geometry}

\name{Val}{Chapman}
\phone[mobile]{779-537-7326}
\email{vchapmanse@gmail.com}
\extrainfo{
 \faGlobe{ valchapman.net }
}

\begin{document}

%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-5mm}
\section{Education}

\cventry{Fall 2014 - May 2018}{Bachelor of Science, Software Engineering}{Iowa State University}{Ames, Iowa}{{}}{GPA: 3.00}%

\cventry{Fall 2012 - 2014}{Associates of Liberal Arts}{Rockvalley College}{Rockford, Illinois}{{}}{GPA: 3.00}%

\section{Employment}
\cventry{December 2016 - Present}{Workiva}{Software Engineer Intern}{Ames, Iowa}{}
{\begin{itemize}
    \item Working on a test automation platform that empowers developers to trust their releases in a CI environment.
    \item Support an always-running platform by communicating problems and solutions directly with the end-users.
    \item Plan and develop new features using Google Cloud, AWS, and Docker, in an agile manner on a large team.
    \item Improving a customizable notification system to deliver messages on production health check test failures.
\end{itemize}}
\cventry{August 2016 - Mqy 2018}{Iowa State University}{Software Engineering Peer Mentor}{Ames, Iowa}{}
{\begin{itemize}
    \item Helped kickstart the peer mentor program for the Iowa State Software Engineering Department by being selected to be in the first group of peer mentors.
    \item Guided a small group of 20 freshmen through their first year at the university.
    \item Provided advice to freshmen, including advice about course scheduling, life on campus, and social issues.
    \item Assisted students through their introductory to programming courses by holding small group meetings and workshops.
    \item Presented on technical topics such as Introduction to Git and Introduction to Web Development.
  \end{itemize}}


\section{Projects}
\cventry{May 2017}{Arduino, C++,}{Bow Range Finder}{}{}
{\begin{itemize}
    \item Built proof of concept for home made bow range finder for a new start-up company.
    \item Gives users the ability acquire range from bow to calculate shots in an instant.
    \item Researched parts and requirements for design of prototype.
    \item Collaborated with 2 team members to to design, implement, and prototype device.
\end{itemize}}
\cventry{May 2017}{php, JavaScript, HTML}{Le Menu}{}{}
{\begin{itemize}
    \item A business solution developed for restaurants to have their menu and ordering service linked directly to customer's electronic device.
    \item Has User Interface to allow for customization of menus by restaurants.
    \item Allows for payment on the website using saved preferences.
\end{itemize}}

\section{Skills}
\subsection{Professional}
\cvlistdoubleitem{Java}{Python}
\cvlistdoubleitem{Docker}{Google Cloud Services}
\subsection{Working}
\cvlistdoubleitem{Dart}{AWS}
\cvlistdoubleitem{JavaScript}{HTML}
\subsection{Experimental}
\cvlistdoubleitem{C/C++}{C\#}
\cvlistdoubleitem{Hadoop Mapreduce}{React}

\section{Extra Curricular Activities}
\begin{itemize}
\item Student Leader - The Salt Company
\item Camp Counselor - Royal Family Kids Camp

\end{itemize}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}
\clearpage
\end{document}